\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
URLifying

\usepackage{fancyhdr, geometry, xspace}
\usepackage[parfill]{parskip}
\geometry{letterpaper,text={7in,9in},centering}
\pagestyle{fancy}

\fancyhead[RO]{Carl Jackson and Max Wang}

@@

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We plan on
reimplementing something similar to \texttt{chownat} (http://samy.pl/chownat/)
for \Trill, which appears to be a standard way to do this.

>>>>

\usepackage{fancyhdr, geometry, hyperref, xspace}
\usepackage[parfill]{parskip}

\geometry{letterpaper,text={7in,9in},centering}
\pagestyle{fancy}

\fancyhead[RO]{Carl Jackson and Max Wang}
\fancyhead[LO]{\url{http://github.com/motmotchat/trill}}

@@

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We plan on
reimplementing something similar to \texttt{chownat}
(\url{http://samy.pl/chownat/}) for \Trill, which appears to be a standard way
to do this.
